Append_smoothed_results

### 2016-11-22 Code/append_smoothed_results.Rmd
append all the smoothed results

```{r load_datasets}
load(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
ktm_smoothed <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/smoothed_results.csv")
```

```{r clean_smoothed_data}
ktm_clean <- ktm_smoothed %>% 
  rename(Race2 = race, Sex2 = sex, State2 = state, COD2 = cod) %>%
  mutate(Age2 = factor(age_bin, levels = c(1:19), 
                       labels = c("<1 year", "1-4 years", "5-9 years", "10-14 years", 
                                  "15-19 years", "20-24 years", "25-29 years", "30-34 years",
                                  "35-39 years", "40-44 years", "45-49 years", "50-54 years", 
                                  "55-59 years", "60-64 years", "65-69 years", "70-74 years", 
                                  "75-79 years", "80-84 years","85+ years"), ordered = T),
         Year2 = factor(year, levels = c(1:45), labels = as.character(1969:2013))
         )
```

```{r merge_results}
dim(dat.clean)
dat.clean <- merge(dat.clean, ktm_clean, 
                   by = c("State2", "Year2", "Race2", "Sex2", "Age2", "COD2"), 
                   all.x = T)
dim(dat.clean)

dat.clean <- dat.clean %>% mutate(Appended_smoothed = ifelse(is.na(X), F, T))

table(dat.clean$Appended_smoothed)
```

@@

diffs <- dat.clean %>% transmute(diff.pop = Population - population, diff.count = Count - deaths)
summary(diffs$diff.pop)
summary(diffs$diff.count)
rm(diffs)
```

@@

```{r compared_original_vs_smoothed2}
dat.clean <- dat.clean %>% mutate(diff.orig.smooth = Count - smoothed_deaths)
summary(dat.clean$diff.orig.smooth)
ggplot(dat.clean, aes(x = diff.orig.smooth)) + geom_density() + geom_rug(alpha = 0.1)
```

@@

```{r calculate_life_expectancy}
#6 mins

@@

```{r calculate_age_decomp_smoothed}
#18 mins

@@

```{r calculate_cod_decomp}
#takes 40 mins

>>>>

```{r load_datasets}
load(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
ktm_smoothed <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/smoothed_results.csv")
ktm_rest <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/smoothed_results_extra_states.csv")
ktm_virginia_males <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/results_males_Virginia_Nov21.csv")

dat.clean <- dat.clean[, -c(31:40)]

head(ktm_smoothed)
head(ktm_rest)
head(ktm_virginia_males)

table(ktm_rest$state == "Virginia")
table(ktm_rest$state)
table(ktm_smoothed$state) #check - i think Mass is in both rest and smoothed so need to remove duplicates.

dim(ktm_rest)
ktm_rest <- ktm_rest %>% filter(state != "Massachusetts") #delete duplicate
dim(ktm_rest)

length(ktm_rest$sex[ktm_rest$state ==  "Virginia" & ktm_rest$sex == "Male"])
dim(ktm_rest)
ktm_rest <- ktm_rest %>% filter(!(state == "Virginia" & sex == "Male"))
dim(ktm_rest)

ktm_virginia_males <- ktm_virginia_males[ , -1]

ktm_all <- rbind(ktm_smoothed, ktm_rest, ktm_virginia_males)
```

```{r clean_smoothed_data}
ktm_clean <- ktm_all %>% 
  rename(Race2 = race, Sex2 = sex, State2 = state, COD2 = cod) %>%
  mutate(Age2 = factor(age_bin, levels = c(1:19), 
                       labels = c("<1 year", "1-4 years", "5-9 years", "10-14 years", 
                                  "15-19 years", "20-24 years", "25-29 years", "30-34 years",
                                  "35-39 years", "40-44 years", "45-49 years", "50-54 years", 
                                  "55-59 years", "60-64 years", "65-69 years", "70-74 years", 
                                  "75-79 years", "80-84 years","85+ years"), ordered = T),
         Year2 = factor(year, levels = c(1:45), labels = as.character(1969:2013))
         )
```

```{r merge_results}
dim(dat.clean)
dat.clean <- merge(dat.clean, ktm_clean, 
                   by = c("State2", "Year2", "Race2", "Sex2", "Age2", "COD2"), 
                   all.x = T)
dim(dat.clean)
dat.clean <- dat.clean %>% mutate(Appended_smoothed = ifelse(is.na(X), F, T))

table(dat.clean$Appended_smoothed)
prop.table(table(dat.clean$Appended_smoothed))
```

@@

dat.clean <- dat.clean %>% mutate(diff.pop = Population - population, diff.count = Count - deaths)
summary(dat.clean$diff.pop)
summary(dat.clean$diff.count)
```

@@

```{r compared_original_vs_smoothed2}
dat.clean <- dat.clean %>% mutate(diff.orig.smooth = Count - smoothed_deaths)
summary(dat.clean$diff.orig.smooth)
ggplot(dat.clean, aes(x = diff.orig.smooth)) + geom_density() + geom_rug(alpha = 0.1)

ggplot(subset(dat.clean, State2 == "Georgia"), aes(x = diff.orig.smooth)) + geom_histogram() + geom_rug(alpha = 0.1) + facet_grid(Sex2~Race2)
ggplot(subset(dat.clean, State2 == "Georgia" & Sex2 == "Male" & Race2 == "Black"), aes(x = diff.orig.smooth)) + geom_histogram() + geom_rug(alpha = 0.1) + facet_wrap(~Age3)

ggplot(subset(dat.clean, State2 == "California"), aes(x = diff.orig.smooth)) + geom_histogram() + geom_rug(alpha = 0.1) + facet_grid(Sex2~Race2)
ggplot(subset(dat.clean, State2 == "California" & Sex2 == "Male" & Race2 == "Black"), aes(x = diff.orig.smooth)) + geom_histogram() + geom_rug(alpha = 0.1) + facet_wrap(~Age3)

ggplot(subset(dat.clean, State2 == "Utah"), aes(x = diff.orig.smooth)) + geom_density() + geom_rug(alpha = 0.1) + facet_grid(Sex2~Race2)
ggplot(subset(dat.clean, State2 == "Utah" & Sex2 == "Male" & Race2 == "Black"), aes(x = diff.orig.smooth)) + geom_histogram() + geom_rug(alpha = 0.1) + facet_wrap(~Age3)
```

@@

```{r calculate_life_expectancy}
#15 mins

@@

```{r calculate_age_decomp_smoothed}
#20 mins

@@

```{r calculate_cod_decomp}
#takes 84 mins
